Reproducible development environments with rix

### 2024-03-28 paper.qmd
a bit of conclusion

>>>>

There are many tools to make one’s analyses reproducible, but Nix distinguishes
itself from these in that its main concern is in deploying
the complete set of packages that are *closed under the ''depends on''
relation*: Nix does not simply install one piece of software,
but its dependencies, and their dependencies. This makes Nix extremely
useful for reproducible research, but because it solves a complex problem,
it is a complex tool. With [rix]{.pkg}, we wish to make using Nix more
accessible by providing a familiar interface and 
user experience to [R]{.proglang} users.
